%----------------------------------------------------------------------------------------
% VIJAY DILIP BARHATE — FRESHER RESUME (1 PAGE)
% ATS-Optimized Jake's Format
%----------------------------------------------------------------------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Custom commands
\newcommand{\resumeItem}[1]{\item\small{#1 \vspace{-2pt}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

\begin{document}

%-----------HEADER-----------
\begin{center}
    \textbf{\Huge \scshape Vijay Dilip Barhate} \\ \vspace{1pt}
    \small +91 9119546691 $|$
    \href{mailto:barhatevinay7777@gmail.com}{barhatevinay7777@gmail.com} $|$
    Kharghar, Navi Mumbai \\
    \href{https://linkedin.com/in/vijay-barhate}{linkedin.com/in/vijay-barhate} $|$
    \href{https://github.com/vijaybarhate}{github.com/vijaybarhate} $|$
    \href{https://vijaybarhate.github.io/portfolio}{vijaybarhate.github.io/portfolio}
\end{center}

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {Saraswati College of Engineering}{Navi Mumbai, India}
    {B.E. in Computer Engineering (Expected 2027)}{2023 -- 2027}
  \resumeSubheading
    {Ambuja Vidya Niketan}{Chandrapur, India}
    {Class XII --- CBSE (CS: 89/100)}{2023}
  \resumeSubheading
    {Manikgarh Cement English School}{Chandrapur, India}
    {Class X --- CBSE (IT: 91/100, Overall: 81.8\%)}{2021}
\resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
    \textbf{Languages}{: Python, SQL (MySQL), Java, TypeScript, JavaScript, HTML, CSS} \\
    \textbf{Libraries \& Frameworks}{: Pandas, Matplotlib, Seaborn, React, Tailwind CSS, Zustand, Framer Motion, GSAP} \\
    \textbf{Tools}{: Git, GitHub, VS Code, MySQL Workbench, Vite} \\
    \textbf{Concepts}{: Data Analysis, Data Visualization, CRUD Applications, DSA, Agile Methodologies}
  }}
\end{itemize}

%-----------SELECTED PROJECTS-----------
\section{Selected Projects}
\resumeSubHeadingListStart
  \resumeSubheading
    {Student Result Analyzer}{\href{https://github.com/vijaybarhate/student-result-analyzer}{\underline{GitHub}}}
    {Python, Pandas, Matplotlib, Seaborn}{Data Analysis}
    \resumeItemListStart
      \resumeItem{Engineered a data analysis pipeline that processes 50+ student records, generating insights like grade distributions, pass/fail ratios, and subject averages.}
      \resumeItem{Designed 5+ modern, publication-ready visual charts utilizing Seaborn to clearly communicate complex datasets.}
      \resumeItem{Architected a scalable CLI using \texttt{argparse} with modular scripts separating data generation and analysis logic.}
    \resumeItemListEnd

  \resumeSubheading
    {SONIVIO Music Player}{\href{https://github.com/vijaybarhate/SONIVIO-Music-Player}{\underline{GitHub}} $|$ \href{https://vijaybarhate.github.io/SONIVIO-Music-Player}{\underline{Live}}}
    {React, TypeScript, Tailwind CSS, Zustand, YouTube Data API v3}{Full-Stack Frontend}
    \resumeItemListStart
      \resumeItem{Developed a high-performance web-based music streaming platform featuring a modern dark-mode aesthetic and seamless YouTube Data API track integration.}
      \resumeItem{Implemented an optimized state management architecture using Zustand, enabling real-time favorites, history, and active track syncing without unnecessary re-renders.}
      \resumeItem{Enhanced UX with complex micro-interactions and smooth page transitions using Framer Motion.}
    \resumeItemListEnd

  \resumeSubheading
    {Expense Tracker with SQL}{\href{https://github.com/vijaybarhate/expense-tracker-sql}{\underline{GitHub}}}
    {Python, MySQL}{Backend \& Database}
    \resumeItemListStart
      \resumeItem{Built a resilient CLI expense tracking application supporting complete CRUD operations and robust persistent MySQL storage.}
      \resumeItem{Optimized SQL query performance to handle 500+ simulated records, enabling real-time category-wise breakdowns and monthly financial summaries.}
    \resumeItemListEnd

  \resumeSubheading
    {School Fee Management System}{\href{https://github.com/vijaybarhate/School-Fee-Management}{\underline{GitHub}}}
    {Python, MySQL, Tabulate}{Database Management}
    \resumeItemListStart
      \resumeItem{Constructed a comprehensive administrative CLI tool managing student profiles and fee transactions using optimized relational JOIN queries across multiple MySQL tables.}
      \resumeItem{Hardened the system against erroneous operations by implementing strict input validation, duplicate fee prevention, and confirmation prompts for destructive actions.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------CERTIFICATIONS & COURSES-----------
\section{Certifications \& Courses}
\resumeSubHeadingListStart
  \resumeSubheading
    {Generative AI Certification}{EduBridge (Capgemini $\times$ SAP $\times$ NSDC)}
    {Comprehensive Generative AI Training}{Feb. 2026}
  \resumeSubheading
    {Generative AI Mastery Workshop}{OpenAI Academy $\times$ NxtWave}
    {Intensive Workshop}{Sep. 2025}
  \resumeSubheading
    {Software Engineering Job Simulation}{Accenture via Forage}
    {Architecture, Security, Programming, Testing \& Agile}{Jun. 2025}
  \resumeSubheading
    {Python Basics to Brilliance Masterclass}{Ethan's Tech Solutions}
    {Python Development}{Apr. 2025}
\resumeSubHeadingListEnd

%-----------EXTRACURRICULAR-----------
\section{Extracurricular Activities}
\resumeSubHeadingListStart
  \resumeSubheading
    {Core Member, Coding Club}{Saraswati College of Engineering}
    {Focus on Data Analytics \& AI/ML initiatives}{2024 -- Present}
  \resumeSubheading
    {Smart India Hackathon (SIH) 2024}{National Level}
    {Developed and pitched a technical government solution as part of a highly competitive team}{2024}
  \resumeSubheading
    {NCC Cadet}{21 MAH BN NCC Wardha, Ministry of Defence}
    {Achieved NCC `A' Certificate with Grade A}{2019 -- 2020}
\resumeSubHeadingListEnd

\end{document}
